\chapter{Conclusions and perspectives}

\section*{Conclusions}

In this dissertation, a novel methodology to model liquid fuel injection in multipoint systems has been proposed. In particular, the focus has been set on atomizers type jet-in-crossflow (JICF). The new injection models, baptised as Smart Lagrangian Injectors (SLI), are able to learn the spray from resolved atomization simulations, and process it to prescribe the liquid phase in dispersed-phase simulations. Two configurations have been studied with this methodology: an academic JICF which served as the development and validation case, and a multi-staged injector named BIMER as the application case. From the first configuration, secondary atomization was found to be the most influential mechanism, since a parametric study on all SLI parameters yielded underestimation of droplets sizes when compared to experiments. Such deviations were caused by the liquid-gas velocities, which were greatly affected by 1) modelling of the gaseous phase disturbances created by dense liquid structures in the lagrangian computations, and 2) the prescription of the liquid velocities at injection. Simulations of BIMER evidenced the strong influence of atomization, since simulations did not capture breakup of lagrangian particles due to droplet equilibrium with the surrounding gas, yielding to a better estimation of experimental droplets sizes. These simulations demonstrate the capability of SLI to learn spray features from resolved simulations of multi-staged injectors and use them to prescribe the liquid phase in dispersed-phase in realistic multi-staged injectors computations. The most significant conclusions extracted from each studied configuration are summarized next.


\subsubsection*{Kerosene jet in crossflow}

In a first step, the theory of the models has been developed and validated in an academic, non-reactive kerosene JICF studied experimentally by \citeColor[becker_breakup_2002]. Resolved atomization simulations were performed with two mesh resolutions at the interface. Firstly, the general physics of the JICF were studied. The resolved simulations could correctly capture the breakup modes (column and surface breakup) observed experimentally for the operating conditions studied. It was found that the finer resolution could capture the jet instabilities at the windward surface while the coarser one did not. It is thought that this is caused by better resolving the gas phase near the interface for the fine, {although this cannot be stated with clarity}. The penetration of the jet was quantified and compared to experimental correlation, revealing the existence of two zones: a near-nozzle region where numerical trajectories matched the experimental correlation, and a far-nozzle area where they deviated further. The first region coincides with the coherent jet, where the dense core is located, while the second one corresponds to the dispersed region where droplets are transported. An analysis of liquid flow rates computed directly from the levelset function showed that fluxes are reduced as the distance from the nozzle increases. It was found that these mass losses were due to small droplets reaching sizes of the order of the mesh resolution, being then removed from the simulation due to the inability of the mesh to transport them further. Secondly, \hl{data necessary to build SLI was obtained from these simulations}. A postprocessing methodology to estimate the dense core breakup coordinates was proposed, which provides input parameters to  later apply the Actuator Line Method (ALM) in dispersed-phase simulation. The resulting spray was finally analyzed in planes perpendicular to the crossflow direction. Droplets were tracked through their center of mass and sampled according to a lagrangian tracking procedure. This methodology could retrieve liquid fluxes similar to the resolved ones. Statistics were obtained for droplets sizes and velocities, which could then be spatially discretized and represented through maps. These local statistics, which showed a good physical behaviour, conform the injectors to prescribe lagrangian droplets in dispersed-phase simulations. \\

Lagrangian simulations for the same configuration were then performed with the SLI built from the resolved simulations. In first place, initial gaseous fields were obtained with two different methodologies to model the disturbance effect of the dense core. The first one, which modelled the dense core through few geometric parameters with 
ALM, was able to capture relevant flow features such as recirculation and deceleration regions, yet it could not retrieve all the characteristics of the flow field. The second methodology, which consisted on prescribing statistics from the gaseous field extracted from the resolved computations in a reduced computational domain, could better capture the overall flow features. Dispersed-phase computations on a high Weber operating point were then performed with SLI for both gaseous methodologies: the prescribed gaseous inlet yielded a better experimental comparison for droplets diameters, probably due to a better estimation of the relative liquid-gas velocities which affected secondary atomization, thus this methodology was selected. The effect of the secondary atomization was studied next, showing that the model chosen can have a strong influence of the spray. The TAB model produced the smallest droplets, followed by the ETAB and the Gorokhovski with tuned model constants, thus the latter one was retrieved. Finally, the different liquid phase parameters were analyzed. The most influential ones were found to be the resolution of resolved simulations and the velocities imposes. A finer resolution yields more converged injectors which, when injected in lagrangian simulations, produce a better experimental comparison independently of the injection location chosen (while for a coarser resolution, this location has a strong influence on the resulting spray). The velocities were found to affect the dispersed phase through two contributions: the estimation of the mean velocity to impose (which produced better results in terms of spray boundaries and ballistic behaviour for a volume-weighted mean than for an arithmetic mean) and the law to prescribe a random component through the RMS velocity (a Gaussian law is recommended). An optimal SLI configuration was selected from all these studies. This one can accurately capture the spray boundaries, the maximum flux location along the $z$ direction and the ballistic behaviour of the spray. On the other hand, the droplets sizes are underestimated in all computations, with a difference of $37~\%$ in the global SMD with respect to experiments. Computations on a lower Weber operating condition showed that the SMD deviations were reduced to $20~\%$. This suggests that the diameter underestimation, which is caused by the secondary atomization, probably arises due to a misprediction of the relative velocities. To assess this hypothesis, an artificial breakup delay was introduced by letting droplets transport for a distance $\Delta x_\mathrm{atom}$ without breaking after injection, allowing them to relax to the gas phase. After this delay, breakup was again triggered. Results show that the size of the resulting droplets increased linearly with the parameter $\Delta x_\mathrm{atom}$, hence the spray SMD approaches the experimental one. On the contrary, the spray showed a counter-ballistic behaviour where the largest droplets were found in the bottom part rather than in the top one. This demonstrates that the size underestimation is caused by an inaccurate prediction of the relative velocities: hence secondary atomization is the most influencing factor in SLI for this configuration. \hl{Future efforts on SLI should focus on better retrieving the relative velocities, by addressing the liquid velocities (e.g. through the sectional approach for droplets size-velocities prescription proposed in} $\S$\ref{subsec:ch5_learning_SLI}) and/or the gaseous ones (e.g. through improvements in the ALM methodology).


\subsubsection*{Swirled injector BIMER}

In a second step, the SLI strategy has been applied to model the take-off stage of the multipoint injector BIMER, tested by \citeColor[renaud_high-speed_2015] at EM2C, which is a configuration more representative of industrial injection systems. Resolved atomization simulations were performed with two interface resolutions on a single injection point from the take-off stage. The liquid jets showed also the two breakup modes present in JICF (column and surface breakup), yet with a rotational component in the jet dynamics due to the swirl component of the air. The jet trajectories showed good agreement with an applicable experimental correlation in the near-nozzle region. Sprays were also analyzed in planes perpendicular to the crossflow, revealing that convergence in droplets sizes is reached both for interface resolution (smallest droplets captured have a size of 30 $\mu$m for both simulations) and for axial distance (constant SMD and invariant histograms at 2 mm downstream the injection nozzle, indicating complete atomization). These sprays were then spatially discretized to yield SLI for liquid fuel injection in lagrangian computations. 

Dispersed-phase computations were performed for the full multi-staged injector BIMER in the last chapter. The pilot stage was simulated with the hollow-cone model FIM-UR. The take-off stage was modelled with the SLI obtained from the resolved atomization simulations previously performed. Even though only one liquid injection point was only resolved, the full take-off stage (composed of 10 injectors) could be simulated by applying the same SLI into each injection hole due to the symmetry of the burner. Three lagrangian computations were performed: one with the gaseous phase modelled with ALM, one with evaporation physics included, and one without any of both. It was found that secondary atomization did not apply in any simulation, since all injected droplets were in equilibrium with the ambient gas. The ALM simulation showed that in this case, the simple model proposed could not retrieve the complex gaseous field from the resolved simulations, probably due to swirl which produced an asymmetric gaseous field not modelled through BIMER. Nevertheless, comparison with the experimental qualitative results on the spray showed no difference when ALM was included or not: this is due to the absence of secondary atomization in BIMER, since this was the biggest influential factor in the academic JICF previously studied. These two simulations showed good experimental agreement qualitatively on the SMD and axial velocity maps, and quantitatively on the global SMD, with differences of less than 30 $\%$. Adding evaporation physics would improve both qualitative and quantitative results, reducing the SMD deviation up to 5 $\%$. These results show the capability of the SLI model to accurately simulate industrial-type multi-staged fuel injectors with reduced cost.




\section*{Perspectives}

These works have contributed to modelling liquid injection in multi-staged injectors. Future works should focus on improving the different modelling blocks of SLI to make dispersed-phase simulations more accurate, and finally to perform combustion simulations with SLI. Therefore, the following perspectives for future extension of this research work are proposed:


\begin{itemize}

	\item Account for more realistic physics in liquid injection parameters. In particular, it is suggested to focus on the following:
	
	\begin{itemize}
	
		\item Accounting for droplet non-sphericity through modified drag coefficients for lagrangian particles \citepColor[bagheri_drag_2016].
		
		\item Prescribing droplets velocities conditioned on their sizes through sectional approaches \citepColor[vie_accounting_2013], which could lead to a better estimation of liquid-gas relative velocities and, therefore, to a more realistic breakup of lagrangian particles caused by the secondary atomization models.
		
		\item Consider transient liquid injection rates for prescribing lagrangian particles fluxes.
	
	\end{itemize}
	
	\item Improve modelling of the dense core disturbance effects. The ALM model could be extended to consider complex geometries and force laws more representative of the jet dense core. The obtention of ALM parameters could also be improved through the employment of multiparameter optimization methods or machine learning tools, such as neural networks. Furthermore, frequential effects could be added to account for the dense core dynamics.
	
	\item Apply the SLI methodology to other atomization configurations, such as the airblast spray resulting from liquid-wall interactions or the hollow cone generated by pressure-swirl atomizers. The latter configuration was modelled in BIMER with the FIM-UR methodology, hence SLI could be employed in this configuration to compare with the results reported in Chapter \ref{ch9:BIMER_lagrangian}. Application to other cases might also require modelling tools different than ALM to address the dense liquid perturbation effects, which are dependent on the atomizer. 
	
	\item Construct the SLI models from extended databases. Current works are focusing on an Eulerian-Lagrangian coupling to convert the droplets from resolved simulations into Lagrangian Point Particles (LPP) that are later transported in the same simulation \citepColor[janodet_numerical_2022]. Thus, the SLI methodology could be applied in these coupled simulations to generate liquid injectors from lagrangian particles in locations further downstream the dense core. Other possibility is to use feed SLI with experimental data on particles when available.  
	
	\item Study the impact of the injection models in reactive simulations, \hl{which is the ultimate goal of any injection model}. In particular, the flexibility for prescription of injection parameters could be used to study the effects of the liquid phase in the evaporation, mixing and combustion processes. In this regard, SLI is a powerful tool to analyze the effect of the liquid phase in reactive phenomena such as ignition, extinction, flame topology, flame-turbulence interaction, thermoacoustic instabilities and pollutant formation. Since BIMER is a reactive test bench which presents extensive experimental results on combustion simulations \citepColor[renaud_high-speed_2015], the SLI developed in this thesis  for this configuration could be used as starting point for these studies.
	



\end{itemize}

